Quality Definitions of Qualities

### 2020-01-19 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
update contact for Ao
update interoperability

\title{Quality Definitions of Qualities} 
\author{Spencer Smith}{McMaster University, Canada}{smiths@mcmaster.ca}{}{}
\author{Jacques Carette}{McMaster University, Canada}{carette@mcmaster.ca}{}{}
\author{Olu Owojaiye}{McMaster University, Canada}{owojaiyo@mcmaster.ca}{}{}
\author{Peter Michalski}{McMaster University, Canada}{michap@mcmaster.ca}{}{}
\author{Ao Dong}{McMaster University, Canada}{}{}{}

@@

\subsection{\done{Interoperability} \ad{owner}}

\begin{defn}
  ``The effort required to couple one system with another''
  \citep{McCallEtAl1977}. (As summarized in \citet{VanVliet2000}.)  \wss{Ao, if
    this is from McCall, we should just cite the primary source and remove the
    Van Vliet reference.} \pmi{Yes this is almost exactly from McCall, except he did not have the word "The" at the beginning.}
\end{defn}

>>>>

\title{Quality Definitions of Qualities} 
\author{Spencer Smith}{McMaster University, Canada}{smiths@mcmaster.ca}{}{}
\author{Jacques Carette}{McMaster University, Canada}{carette@mcmaster.ca}{}{}
\author{Olu Owojaiye}{McMaster University, Canada}{owojaiyo@mcmaster.ca}{}{}
\author{Peter Michalski}{McMaster University, Canada}{michap@mcmaster.ca}{}{}
\author{Ao Dong}{McMaster University, Canada}{donga9@mcmaster.ca}{}{}

@@

\subsection{\notdone{Interoperability} \ad{owner}}

\begin{defn}
  Effort required to couple one system with another
  \citep{McCallEtAl1977}. \wss{Ao, if
    this is from McCall, we should just cite the primary source and remove the
    Van Vliet reference.} \pmi{Yes this is almost exactly from McCall, except he did not have the word "The" at the beginning.}
    \ad{Someone with access to the book added it. I found the book in the pub folder and fixed it.}
\end{defn}
